%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Simple LaTeX CV Template %%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% NOTE: If you find that it says                                     %%
%%                                                                    %%
%%                           1 of ??                                  %%
%%                                                                    %%
%% at the bottom of your first page, this means that the AUX file     %%
%% was not available when you ran LaTeX on this source. Simply RERUN  %%
%% LaTeX to get the ``??'' replaced with the number of the last page  %%
%% of the document. The AUX file will be generated on the first run   %%
%% of LaTeX and used on the second run to fill in all of the          %%
%% references.                                                        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't like 10pt? Try 11pt or 12pt
\documentclass[10pt]{article}

% This is a helpful package that puts math inside length specifications
\usepackage{calc}

\usepackage{soul}

% Simpler bibsection for CV sections
% (thanks to natbib for inspiration)
\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{1em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newenvironment{bibsection}
    {\minipage[t]{\linewidth}\list{}{%
        \setlength{\leftmargin}{\bibhang}%
        \setlength{\itemindent}{-\leftmargin}%
        \setlength{\itemsep}{\bibsep}%
        \setlength{\parsep}{\z@}%
        }}
    {\endlist\endminipage}
\makeatother

% Layout: Puts the section titles on left side of page
\reversemarginpar

%
%         PAPER SIZE, PAGE NUMBER, AND DOCUMENT LAYOUT NOTES:
%
% The next \usepackage line changes the layout for CV style section
% headings as marginal notes. It also sets up the paper size as either
% letter or A4. By default, letter was used. If A4 paper is desired,
% comment out the letterpaper lines and uncomment the a4paper lines.
%
% As you can see, the margin widths and section title widths can be
% easily adjusted.
%
% ALSO: Notice that the includefoot option can be commented OUT in order
% to put the PAGE NUMBER *IN* the bottom margin. This will make the
% effective text area larger.
%
% IF YOU WISH TO REMOVE THE ``of LASTPAGE'' next to each page number,
% see the note about the +LP and -LP lines below. Comment out the +LP
% and uncomment the -LP.
%
% IF YOU WISH TO REMOVE PAGE NUMBERS, be sure that the includefoot line
% is uncommented and ALSO uncomment the \pagestyle{empty} a few lines
% below.
%

%% Use these lines for letter-sized paper
\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=1.2in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1in,               % 1 inch margins
            includemp]{geometry}

%% Use these lines for A4-sized paper
%\usepackage[paper=a4paper,
%            %includefoot, % Uncomment to put page number above margin
%            marginparwidth=30.5mm,    % Length of section titles
%            marginparsep=1.5mm,       % Space between titles and text
%            margin=25mm,              % 25mm margins
%            includemp]{geometry}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

%% This gives us fun enumeration environments. compactitem will be nice.
\usepackage{paralist}

%% Reference the last page in the page number
%
% NOTE: comment the +LP line and uncomment the -LP line to have page
%       numbers without the ``of ##'' last page reference)
%
% NOTE: uncomment the \pagestyle{empty} line to get rid of all page
%       numbers (make sure includefoot is commented out above)
%
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
%\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

% Finally, give us PDF bookmarks
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

%%%%%%%%%%%%%%%%%%%%%%%% End Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%% Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The title (name) with a horizontal rule under it
%
% Usage: \makeheading{name}
%
% Place at top of document. It should be the first thing.
\newcommand{\makeheading}[1]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
                {\large \bfseries #1}\\[-0.15\baselineskip]%
                 \rule{\columnwidth}{1pt}%
         \end{minipage}}

% The section headings
%
% Usage: \section{section name}
%
% Follow this section IMMEDIATELY with the first line of the section
% text. Do not put whitespace in between. That is, do this:
%
%       \section{My Information}
%       Here is my information.
%
% and NOT this:
%
%       \section{My Information}
%
%       Here is my information.
%
% Otherwise the top of the section header will not line up with the top
% of the section. Of course, using a single comment character (%) on
% empty lines allows for the function of the first example with the
% readability of the second example.
\renewcommand{\section}[2]%
        {\pagebreak[2]\vspace{1.3\baselineskip}%
         \phantomsection\addcontentsline{toc}{section}{#1}%
         \hspace{0in}%
         \marginpar{
         \raggedright \scshape #1}#2}

% An itemize-style list with lots of space between items
\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1]}{\end{itemize}%
         \vspace{-.6\baselineskip}}

% An environment IDENTICAL to outerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactitem}[#1]}{\end{compactitem}}

% To add some paragraph space between lines.
% This also tells LaTeX to preferably break a page on one of these gaps
% if there is a needed pagebreak nearby.
\newcommand{\blankline}{\quad\pagebreak[2]}

% 

%%%%%%%%%%%%%%%%%%%%%%%% End Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\makeheading{Adam Procter, Ph.D.}

\section{Contact}
%
% NOTE: Mind where the & separators and \\ breaks are in the following
%       table.
%
% ALSO: \rcollength is the width of the right column of the table
%       (adjust it to your liking; default is 1.85in).
%
\newlength{\rcollength}\setlength{\rcollength}{2.0in}%
%
\begin{tabular}[t]{@{}p{\textwidth-\rcollength}p{\rcollength}}
\href{mailto:adamprocter@mail.missouri.edu}{adamprocter@mail.missouri.edu} & \href{https://github.com/aprocter}{https://github.com/aprocter}\\
+1 573 819 2767 & \href{http://adamprocter.com/}{http://adamprocter.com}\\
\end{tabular}

%\section{Summary}
%
%To obtain a post-doctoral position in the academic, government, or private sector that draws on my demonstrated talent for cutting-edge research in programming languages, program verification, and information security.

\section{Summary}
%
Experienced software engineer with a strong background in programming language and systems research and a proven track record of delivering solutions for highly demanding customers in the machine learning space. Interests include deep learning, compiler architecture, functional programming, semantics of programming languages, hardware synthesis from functional languages, model-driven implementation techniques for secure systems, and computer-assisted theorem proving.

\section{Employment}
%
\textbf{\href{https://groq.com/}{Groq, Inc.}}
\begin{outerlist}
\item[] \textit{Compiler Engineer} \hfill October 2019---present
        \begin{innerlist}
        \item Contributed to the development of front-end compiler infrastructure.
        \item Revamped integration with popular deep learning frameworks, resulting in a greatly improved user experience.
        \item Improved testing infrastructure and coverage for both front-end and back-end compiler components.
        \item Developed core components of the low-level Groq runtime.
        \item Drove roadmap discussions for the Groq software stack as part of rapid go-to-market efforts.
        \item Formalized and documented coding and process standards for a growing software team.
        \end{innerlist}
\end{outerlist}

\blankline

\textbf{\href{https://www.intel.com/}{Intel Corporation}}
\begin{outerlist}
\item[] \textit{Deep Learning Software Engineer} \hfill September 2017---October 2019
        \begin{innerlist}
        \item Core software engineer for nGraph, an open-source compiler for deep learning models which supports many frameworks and hardware targets.
        \item Defined semantics of core nGraph intermediate representation.
        \item Designed and implemented most front-end APIs for graph construction, and many other parts of the compiler front-end.
        \item Made major contributions to the nGraph-TensorFlow bridge, which allows TensorFlow models to run within the framework on nGraph-accelerated backends.
        \item Advocated for a high standard of modularity, code quality, test-driven development, and correctness by construction.
        \item Represented the nGraph project at major external forums including the NeurIPS Expo and the O'Reilly AI Conference.
        \item Mentored numerous junior engineers contributing to the nGraph project.
        \end{innerlist}
\item[] \textit{Machine Learning Engineer} \hfill June 2016---September 2017
        \begin{innerlist}
        \item Gathered extensive, detailed, replicable benchmarking results for numerous popular deep learning workloads on pre-launch next-generation Xeon processors, which formed a major part of marketing collateral at launch.
        \item Developed detailed performance tuning recommendations for customers running deep learning training workloads on Intel Xeon and Xeon Phi-based clusters.
        \item Assisted several customers with setup and performance tuning of deep learning training on Intel Xeon and Xeon Phi-based clusters.
        \item Developed compelling demos of deep learning training performance for trade shows and various other public venues.
        \item Contributed to the development of deep learning accelerator IP for FPGAs.
        \end{innerlist}
\end{outerlist}

\blankline

\textbf{\href{http://www.missouri.edu/}{University of Missouri}}
\begin{outerlist}
\item[] \textit{Postdoctoral Fellow} \hfill November 2014---May 2015
        \begin{innerlist}
        \item Postdoctoral researcher at the Center for High Assurance Computing.
        \item Developed mechanized metatheory for ReWire, a purely functional language for provably secure hardware designs.
        \item Research published in high-profile conferences and journals (LCTES, TECS).
        \item Supervisor: Professor William L. Harrison.
        \end{innerlist}
\item[] \textit{GAANN Graduate Fellow} \hfill January 2011---November 2014\\
        \textit{Graduate Research Assistant} \hfill June 2008---December 2010
        \begin{innerlist}
        \item Research assistant at the High Assurance Security Kernel (HASK) Lab, under Professor William L. Harrison.
        \item Developed the ReWire compiler, which translates a subset of Haskell to synthesizable implementations of provably secure hardware.
        \end{innerlist}
\item[] \textit{Graduate Teaching Assistant} \hfill August 2005---May 2008\\
        \color{white}.\color{black}          \hfill August 2009---December 2009\\
        \color{white}.\color{black}          \hfill August 2010---December 2010
        \begin{innerlist}
        \item Served as instructor or teaching assistant for several diferent computer science courses.
        \item Courses taught include Problem Solving and Programming I (CS 101), Compilers, and Principles of Programming Languages.
        \item Duties ranged from grading and holding office hours to teaching a large lecture course and supervising four teaching assistants.
        \end{innerlist}
\end{outerlist}

\blankline

\textbf{\href{http://www.cs.uiowa.edu/}{Department of Computer Science}, University of Iowa}
\begin{outerlist}
\item[] \textit{Short-Term Scientific Employee (Summer Visitor)} \hfill June 2010---August 2010
        \begin{innerlist}
        \item Developed a theorem-proving system for monadic programs in collaboration with Professor Aaron Stump.
        \end{innerlist}
\end{outerlist}

%% \blankline

%% \textbf{\href{http://www.biology.missouri.edu/}{Division of Biological Sciences}, University of Missouri}
%% \begin{outerlist}
%% \item[] \textit{Computer Programmer} \hfill June 2006---May 2009
%%         \begin{innerlist}
%%         \item Developed a LabVIEW-based application to play back aural stimuli to insects in support of behavioral and neurological experiments.
%%         \end{innerlist}
%% \end{outerlist}

%% \blankline

%% \textbf{\href{http://japanesestudies.missouri.edu/}{Japanese Studies Program}, University of Missouri}
%% \begin{outerlist}
%% \item[] \textit{Peer Learning Assistant} \hfill August 2004---May 2005
%%         \begin{innerlist}
%%         \item Served as co-instructor for Elementary Japanese II in Spring 2005.
%%         \item Conducted two weekly lab sessions for Elementary Japanese I in Fall 2004.
%%         \end{innerlist}
%% \end{outerlist}

%% \blankline

%% \textbf{\href{http://success.missouri.edu/tlc.html}{The Learning Center}, University of Missouri}
%% \begin{outerlist}
%% \item[] \textit{Tutor} \hfill June 2002---May 2004
%%         \begin{innerlist}
%%         \item Tutored individual students in computer science and elementary Japanese.
%%         \item Held group tutoring sessions in computer science.
%%         \end{innerlist}
%% \end{outerlist}

\section{Education}
%
\textbf{\href{http://www.missouri.edu/}{University of Missouri}},
Columbia, Missouri USA
\begin{outerlist}

\item[] Ph.D.,
        \href{http://www.cs.missouri.edu/}
             {Computer Science}, December 2014. Advisor: William L. Harrison.
        \begin{innerlist}
        \item Dissertation: {\em Semantics-Driven Design and Implementation of High-Assurance Hardware}
%        \item Advisor: William L. Harrison}
%        \item GPA: 3.96/4.00
        \end{innerlist}

\item[] B.A.,
        \href{http://www.cs.missouri.edu/}
             {Computer Science}, \emph{summa cum laude}, minor in \href{http://www.math.missouri.edu/}{Mathematics}, May 2005.
%%         \begin{innerlist}
%%         \item Minor in 
%%         \item Graduated \emph{summa cum laude}
%% %        \item GPA: 3.91/4.00
%%         \end{innerlist}

\end{outerlist}

\section{Publications}
%
\begin{bibsection}
    \item Thomas N. Reynolds, Adam Procter, William L. Harrison, and Gerard Allwein. \ul{The Mechanized Marriage of Effects and Monads with Applications to High-assurance Hardware.}
        \emph{ACM Transactions on Embedded Computing Systems (TECS) - Special Issue on MEMOCODE 2017 and Regular Papers}, volume 18, issue 1, February 2019.
  
    \item Scott Cyphers, Arjun K. Bansal, Anahita Bhiwandiwalla, Jayaram Bobba, Matthew Brookhart, Avijit Chakraborty, Will Constable, Christian Convey, Leona Cook, Omar Kanawi, Robert Kimball, Jason Knight, Nikolay Korovaiko, Varun Kumar, Yixing Lao, Christopher R. Lishka, Jaikrishnan Menon, Jennifer Myers, Sandeep Aswath Narayana, Adam Procter, and Tristan J. Webb. \ul{Intel nGraph: An Intermediate Representation, Compiler, and Executor for Deep Learning.}
        \emph{SysML Conference 2018}, February 2018. \href{https://arxiv.org/abs/1801.08058}{https://arxiv.org/abs/1801.08058}

    \item Yuankun Shi, Kevin Long, Kaushik Balasubramanian, Bianny Bian, Adam Procter, and Ramesh Illikkal.
        \ul{DeepSim: Cluster Level Behavioral Simulation Model for Deep Learning.}
        \emph{2017 IEEE 15th Intl Conf on Dependable, Autonomic and Secure Computing, 15th Intl Conf on Pervasive Intelligence and Computing, 3rd Intl Conf on Big Data Intelligence and Computing and Cyber Science and Technology Congress(DASC/PiCom/DataCom/CyberSciTech)}, November 2017.

    \item Thomas N. Reynolds, Adam Procter, William L. Harrison, and Gerard Allwein. \ul{A core calculus for secure hardware: its formal semantics and proof system.}
        \emph{Proceedings of the 15th ACM-IEEE International Conference on Formal Methods and Models for System Design (MEMOCODE'17)}, September 2017.

    \item Adam Procter, William L. Harrison, Ian Graves, Michela Becchi, and Gerard Allwein. \ul{A Principled Approach to Secure Multi-core Processor Design with ReWire.}
        \emph{ACM Transactions on Embedded Computing Systems (TECS) - Special Issue on LCTES 2015, Special Issue on ACSD 2015 and Special Issue on Embedded Devise Forensics and Security}, volume 16, issue 2, April 2017.

    \item William L. Harrison, Adam Procter, and Gerard Allwein. \ul{Model-driven design \& synthesis of the SHA-256 cryptographic hash function in ReWire.}
        \emph{Proceedings of the 27th International Symposium on Rapid System Prototyping: Shortening the Path from Specification to Prototype (RSP'16)}, October 2016.

    \item Ian Graves, Adam Procter, Wililam L. Harrison, Michela Becchi, and Gerard Allwein. \ul{Provably Correct Development of Reconfigurable Hardware Designs via Equational Reasoning.}
	\emph{Proceedings of the 2015 International Conference on Field-Programmable Technology (ICFPT'15)}, Queenstown, New Zealand, December 2015.

    \item Adam Procter, William L. Harrison, Ian Graves, Michela Becchi, and Gerard Allwein. \ul{Semantics Driven Hardware Design, Implementation, and Verification with ReWire.}
        \emph{Proceedings of the 2015 ACM SIGPLAN/SIGBED Conference on Languages, Compilers, Tools and Theories for Embedded Systems (LCTES'15)}, Portland, June 2015.

    \item Ian Graves, Adam Procter, William L. Harrison, Michela Becchi, and Gerard Allwein. \ul{Hardware Synthesis from Functional Embedded Domain-Specific Languages: A Case Study in Regular Expression Compilation.}
        \emph{Proceedings of the 11th International Symposium on Applied Reconfigurable Computing (ARC'15)}, Bochum, April 2015.

    \item Adam Procter, William L. Harrison, Ian Graves, Michela Becchi, and Gerard Allwein. \ul{Semantics-directed Machine Architecture in ReWire.}
        \emph{Proceedings of the 2013 International Conference on Field-Programmable Technology (ICFPT'13)}, Kyoto, December 2013.

\end{bibsection}

\section{Publications cont'd}
%
\begin{bibsection}

    \item William L. Harrison, Adam Procter, and Gerard Allwein. \ul{The Confinement Problem in the Presence of Faults.}
        \emph{Proceedings of the 14th International Conference on Formal Engineering Methods (ICFEM'12)}, Kyoto, November 2012.

    \item Chris Hathhorn, Michela Becchi, William L. Harrison and Adam Procter. \ul{Formal semantics of heterogeneous CUDA-C: A modular approach with applications.}
        \emph{Proceedings of the 2012 Systems Software Verification Conference (SSV'12)}, Sydney, November 2012.

    \item Adam Procter, William L. Harrison, and Aaron Stump. \ul{The Design of a Practical Theorem Prover for a Lazy Functional Language.}
        \emph{Proceedings of the 2012 Symposium on Trends in Functional Programming (TFP'12)}, St Andrews, UK, June 2012.

    \item Michela Becchi, Kittisak Sajjapongse, Ian Graves, Adam Procter, Vignesh Ravi, and Srimat Chakradhar.
            \ul{A Virtual Memory Based Runtime to Support Multitenancy in Clusters with GPUs.} \emph{Proceedings of the 21st International Symposium on High-Performance Parallel and Distributed Computing (HPDC'12)}, Delft, June 2012. {\bf (Best paper award!)}

    \item William L. Harrison, Benjamin Schulz, Adam Procter, Andrew Lukefahr, and Gerard Allwein.
        \ul{Towards Semantics-directed System Design and Synthesis.} Invited
        paper. \emph{Proceedings of the 2011 International Conference on Engineering of Reconfigurable Systems and Algorithms (ERSA'11)}, Las Vegas, July 2011.

    \item William L. Harrison, Adam M. Procter, Jason Agron, Garrin Kimmell, and Gerard Allwein.
        \ul{Model-driven Engineering from Modular Monadic Semantics: Implementation
        Techniques Targeting Hardware and Software.} \emph{Proceedings of the IFIP
        Working Conference on Domain Specific Languages (DSLWC)}, Oxford, July 2009.

    \item Pericles S. Kariotis, Adam M. Procter, and William L. Harrison. \ul{Making
        Monads First-class with Template Haskell.} \emph{Proceedings of the ACM
        SIGPLAN 2008 Haskell Symposium (Haskell '08)}, Victoria, BC, Canada, September 2008.

    \item William L. Harrison, Gerard Allwein, Andy Gill, and Adam Procter.
        \ul{Asynchronous Exceptions as an Effect.} \emph{Proceedings of the Ninth
        International Conference on Mathematics of Program Construction (MPC'08)},
        Marseille, July 2008.
\end{bibsection}

\section{Presentations}
%
\begin{bibsection}
    \item Adam Procter.
      \ul{nGraph: Unlocking Next-generation Performance with Deep Learning Compilers.} Intel AI Developer Webinar Series, August 2019.

    \item Adam Procter, Adam Straw, and Robert Earhart.
      \ul{nGraph: Unlocking next-generation performance with deep learning compilers.} O'Reilly Artificial Intelligence Conference, New York, April 2019.

    \item Adam Procter, Adam Straw, and Robert Earhart.
      \ul{Intel nGraph: Unlocking Next-Generation Performance with Deep Learning Compilers.} NeurIPS Expo, December 2018.
\end{bibsection}

\section{Professional Service}
%
\vspace{-1em}
\begin{innerlist}
\item External reviewer for IFL'11.
\item Helped organize Midwest Verification Day 2014 in Columbia, MO.
\end{innerlist}

%% \section{Teaching Experience}
%% %
%% \textbf{\href{http://www.cs.missouri.edu/}{Department of Computer Science}, University of Missouri}
%% \begin{innerlist}
%% \item Instructor, Principles of Programming Languages, Fall 2010 and Fall 2012
%% \item Teaching Assistant, Principles of Programming Languages, Fall 2009, Spring 2008, and Spring 2007
%% \item Teaching Assistant, Production Languages (Programming in C), Fall 2007 and Fall 2006
%% \item Instructor, Production Languages (Programming in C), Spring 2007
%% \item Instructor, Algorithm Design and Programming I, Spring 2006
%% \item Teaching Assistant, Algorithm Design and Programming I, Fall 2005
%% \end{innerlist}

%% \blankline

%% \textbf{\href{http://japanesestudies.missouri.edu/}{Japanese Studies Program}, University of Missouri}
%% \begin{innerlist}
%% \item Instructor, Elementary Japanese II, Spring 2005
%% \item Teaching Assistant, Elementary Japanese I, Fall 2004
%% \end{innerlist}

%% \blankline

%% \textbf{\href{http://success.missouri.edu/tlc.html}{The Learning Center}, University of Missouri}
%% \begin{innerlist}
%% \item Tutor, Summer 2002---Spring 2004
%% \end{innerlist}

%% \section{Honors and Awards}
%% %
%% Fellowships and Scholarships
%% \begin{innerlist}
%% \item Graduate Assistance in Areas of National Need (GAANN) Fellowship, 2011---2014
%% \item Gilliom Graduate Fellowship in Cyber Security, 2007---2009
%% \item State of Missouri Bright Flight Scholarship, 2000---2005
%% \end{innerlist}

%% \blankline

%% Honors
%% \begin{innerlist}
%% \item Honorary student marshal, University of Missouri College of Arts and Science commencement ceremony, May 2005
%% \item University of Missouri College of Arts and Science dean's list every semester, Fall 2000---Spring 2005
%% \item Phi Beta Kappa (junior-year inductee, 2003)
%% \end{innerlist}

\section{Technical \,\,\,\,Skills}
%
Languages
\begin{innerlist}
\item C++, C, Haskell, Standard ML, Coq, Python, Java, JavaScript, HTML/CSS, PHP, Perl, UNIX shell scripting.
\end{innerlist}

\blankline

Machine Learning Frameworks
\begin{innerlist}
\item TensorFlow, Caffe, PaddlePaddle.
\end{innerlist}

\blankline

Methodologies
\begin{innerlist}
\item Agile development, test-driven development.
\end{innerlist}

%\section{Activities and Volunteer Work}
%
%Volunteer system administration for Mizzou Linux Users Group

%\blankline

%Miscellaneous computer support tasks for \href{http://www.gromo.org/}{GRO -- Grass Roots Organizing}, a not-for-profit social justice organization

\section{Languages}
%
English (native speaker)

Japanese (read, write, and speak at a high intermediate to advanced level)

German (once intermediate, now quite rusty)

%\section{References}
%
%Available upon request.

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%% End CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
